---
title: "Verifying the diagnosis coding using randomly selected women. 2019 data."
author: "Adrian Barnett"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

  
```{r, include=FALSE}
# called from 1_diagnosis.R

knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, comment='', dpi=400)
options(width=1000) # Wide pages
options(scipen=999) # avoid scientific presentation
library(dplyr)
library(janitor)
library(flextable)
set_flextable_defaults(big.mark='') 
n_sample = 5 # number to sample
TeachingDemos::char2seed('barrow')

# randomly sample mothers, just those with 1 pregnancy
single_pregnancy = group_by(diagnosis_2019, mother_id) %>%
  summarise(pregs = max(preg_seq_id  )) %>%
  ungroup() %>%
  filter(pregs == 1) %>%
  select(mother_id)
to_sample = left_join(single_pregnancy, diagnosis_2019, by='mother_id')
# a) missing
sample_NA = filter(to_sample, is.na(early_gdm) & is.na(gdm)) %>%
  filter(facility_name =="Royal Brisbane and Women's") %>% # temporary
  sample_n(n_sample) %>%
  select(mother_id)
# b) not missing and with positive diagnosis
sample_positive = filter(to_sample, early_gdm == 'Yes' | gdm =='Yes') %>%
  sample_n(n_sample) %>%
  select(mother_id)
# c) not missing and with negative diagnosis
sample_negative = filter(to_sample, early_gdm == 'No' | gdm =='No') %>%
  sample_n(n_sample) %>%
  select(mother_id)
```

We take random samples of the data to examine how Adrian's diagnosis coding has worked. For simplicity we exclude women who had two pregnancies in the same year.

# Missing data for GDM diagnosis

First we look at missing GDM diagnosis (using my derivation) by facility. The cells show the missing numbers and within-facility percentage of missing. The rows are arranged by the percent missing.

```{r}
tab = mutate(diagnosis_2019, missing = is.na(gdm) & is.na(early_gdm),
             missing = ifelse(missing==TRUE, 'Missing','Not missing')) %>%
  group_by(facility_name, missing) %>%
  tally() %>%
  group_by(facility_name) %>%
  mutate(percent = round(prop.table(n)*100)) %>%
  filter(missing == 'Missing') %>%
  arrange(desc(percent))
ftab = flextable(tab) %>%
  fontsize(part = 'all', size = 8) %>%
  autofit() 
ftab
```

<!--- Almost all the women in private hospitals have missing OGTT data. We could possibly exclude these women from the analysis? --->

# Examples with missing GDM and early GDM diagnosis

### Selected variable from mother data

```{r}
to_table = left_join(sample_NA, mother_data, by = c('mother_id')) %>%
  select(mother_id, facility_name, est_confinment_date, body_mass_index, pregnancy_complicatns_flag, gdm_diagnosis) %>%
  arrange(mother_id)
tab = flextable(to_table) %>%
  fontsize(part = 'all', size = 8) %>%
  autofit()
tab
```

### Glucose data

```{r}
to_table = left_join(sample_NA, mother_glu, by = c('mother_id')) %>%
  select(-source) %>%
  arrange(mother_id, collected)
tab = flextable(to_table) %>%
  fontsize(part = 'all', size = 9) %>%
  merge_v(j=1) %>%
  theme_box() %>%
  autofit()
tab
```


### a1c data

```{r}
to_table = left_join(sample_NA, mother_a1c, by = c('mother_id')) %>%
  select(-source) %>%
  arrange(mother_id, collected)
tab = flextable(to_table) %>%
  fontsize(part = 'all', size = 9) %>%
  merge_v(j=1) %>%
  theme_box() %>%
  autofit()
tab
```


# Examples with positive GDM or early GDM diagnosis

### Selected variable from mother data

```{r}
to_table = left_join(sample_positive, mother_data, by = c('mother_id')) %>%
  select(mother_id, facility_name, est_confinment_date, body_mass_index, pregnancy_complicatns_flag, gdm_diagnosis) %>%
  arrange(mother_id)
tab = flextable(to_table) %>%
  fontsize(part = 'all', size = 8) %>%
  autofit()
tab
```

### Glucose data

```{r}
to_table = left_join(sample_positive, mother_glu, by = c('mother_id')) %>%
  select(-source) %>%
  arrange(mother_id, collected)
tab = flextable(to_table) %>%
  fontsize(part = 'all', size = 9) %>%
  merge_v(j=1) %>%
  theme_box() %>%
  autofit()
tab
```

### a1c data

```{r}
to_table = left_join(sample_positive, mother_a1c, by = c('mother_id')) %>%
  select(-source) %>%
  arrange(mother_id, collected)
tab = flextable(to_table) %>%
  fontsize(part = 'all', size = 9) %>%
  merge_v(j=1) %>%
  theme_box() %>%
  autofit()
tab
```

### Diagnosis data (derived by Adrian)

```{r}
to_table = left_join(sample_positive, diagnosis_2019, by = c('mother_id')) %>%
  select(mother_id, ogtt, early_gdm, gdm) %>%
  arrange(mother_id)
tab = flextable(to_table) %>%
  fontsize(part = 'all', size = 9) %>%
  merge_v(j=1) %>%
  theme_box() %>%
  autofit()
tab
```

# Examples with negative GDM or early GDM diagnosis

### Selected variable from mother data

```{r}
to_table = left_join(sample_negative, mother_data, by = c('mother_id')) %>%
  select(mother_id, facility_name, est_confinment_date, body_mass_index, pregnancy_complicatns_flag, gdm_diagnosis) %>%
  arrange(mother_id)
tab = flextable(to_table) %>%
  fontsize(part = 'all', size = 8) %>%
  autofit()
tab
```

### Glucose data

```{r}
to_table = left_join(sample_negative, mother_glu, by = c('mother_id')) %>%
  select(-source) %>%
  arrange(mother_id, collected)
tab = flextable(to_table) %>%
  fontsize(part = 'all', size = 9) %>%
  merge_v(j=1) %>%
  theme_box() %>%
  autofit()
tab
```

### a1c data

```{r}
to_table = left_join(sample_negative, mother_a1c, by = c('mother_id')) %>%
  select(-source) %>%
  arrange(mother_id, collected)
tab = flextable(to_table) %>%
  fontsize(part = 'all', size = 9) %>%
  merge_v(j=1) %>%
  theme_box() %>%
  autofit()
tab
```

### Diagnosis data (derived by Adrian)

```{r}
to_table = left_join(sample_negative, diagnosis_2019, by = c('mother_id')) %>%
  select(mother_id, ogtt, early_gdm, gdm) %>%
  arrange(mother_id)
tab = flextable(to_table) %>%
  fontsize(part = 'all', size = 9) %>%
  merge_v(j=1) %>%
  theme_box() %>%
  autofit()
tab
```

