---
title: "Are changes to Gestational Diabetes Mellitus screening and diagnosis during COVID-19 worth continuing?\nSummary statistics"
author: "Adrian Barnett"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

  
```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, comment='', dpi=400)
options(width=1000) # Wide pages
options(scipen=999) # avoid scientific presentation
library(vtable)
library(dplyr)
library(tidyr)
library(flextable)
library(janitor)
library(ggplot2)
library(scales) # for date_format

# load the data
load('data/raw_data.RData')
```

Queensland Perinatal Data Collection (PDC):  Mother and baby records for births between (1 July 2019 and 31 December 2019) and (1 July 2020 and 31 December 2020). 

# Baby data

```{r}
for_table = select(baby_data, -ends_with('_id'), -source)
sumtable(for_table,
         title  = '',
         digits = 0)
```

### Baby data - histograms of continuous variables 

```{r}
for_plot = select_if(for_table, is.numeric) %>%
  pivot_longer(cols=everything())
gplot = ggplot(data=for_plot, aes(x=value))+
  geom_histogram()+
  facet_wrap(~name, scales='free')+
  theme_bw()
gplot
```


# Baby induction

Method of inducing labour or augmenting labour after spontaneous onset

```{r}
assist = baby_lab_assist$induction_method
tab = tabyl(assist) %>%
  arrange(-n) %>%
  mutate(percent = round(percent*100))
ftab = flextable(tab) %>%
  theme_box() %>%
  autofit()
ftab
```
# Baby complication

A medical or obstetric complication arising during labour as represented by a code.

```{r}
complication = baby_lab_deliv_compln$labour_deliv_complicatn_text
tab = tabyl(complication) %>%
  arrange(-n) %>%
  mutate(percent = round(percent*100))
ftab = flextable(tab) %>%
  theme_box() %>%
  autofit()
ftab
```

# Baby resuscitation

Active measure taken immediately after birth to establish independent respiration and heart beat, or to treat depressed respiratory effort and to correct metabolic disturbances

```{r}
resuscitation = baby_resuscitation$resuscitation
tab = tabyl(resuscitation) %>%
  arrange(-n) %>%
  mutate(percent = round(percent*100))
ftab = flextable(tab) %>%
  theme_box() %>%
  autofit()
ftab
```

# Baby morbidity

The description of a condition or disease of the baby present prior to discharge, transfer or death, as represented by a code.

```{r}
morbidity = baby_neonatal_morb$neonatal_morbidity_code_text
tab = tabyl(morbidity) %>%
  arrange(-n) %>%
  mutate(percent = round(percent*100))
ftab = flextable(tab) %>%
  theme_box() %>%
  autofit()
ftab
```

# Baby treatment

The type of neonatal treatment given during the birth episode.

```{r}
treatment = baby_neonatal_treat$neonatal_treatment
tab = tabyl(treatment) %>%
  arrange(-n) %>%
  mutate(percent = round(percent*100))
ftab = flextable(tab) %>%
  theme_box() %>%
  autofit()
ftab
```

# Baby feeding

Any feeding method other than breast feeding used prior to discharge.

```{r}
feeding = baby_alt_feed_method$alternative_feed_method
tab = tabyl(feeding) %>%
  arrange(-n) %>%
  mutate(percent = round(percent*100))
ftab = flextable(tab) %>%
  theme_box() %>%
  autofit()
ftab
```

# Mother data

```{r}
for_table = select(mother_data, -ends_with('_id'), -source)
sumtable(for_table,
         title  = '',
         digits = 0)
```

### Mother data - histograms of continuous variables 

```{r}
for_plot = select_if(for_table, is.numeric) %>%
  pivot_longer(cols=everything())
gplot = ggplot(data=for_plot, aes(x=value))+
  geom_histogram()+
  facet_wrap(~name, scales='free')+
  theme_bw()
gplot
```

# Mother last birth methods

```{r}
for_table = select(mother_deliv_last_brth, -ends_with('_id'), -source)
sumtable(for_table,
         title  = '',
         digits = 0)
```

# Mother pregnancy complications

```{r}
complication = mother_preg_complicatn$pregnancy_complication_text
tab = tabyl(complication) %>%
  arrange(-n) %>%
  mutate(percent = round(percent*100))
ftab = flextable(tab) %>%
  theme_box() %>%
  autofit()
ftab
```

# Mother existing medical conditions

```{r}
condition = mother_existing_medi_condtns$medical_condition_text
tab = tabyl(condition) %>%
  arrange(-n) %>%
  mutate(percent = round(percent*100))
ftab = flextable(tab) %>%
  theme_box() %>%
  autofit()
ftab
```

# Mother transfer reasons

```{r}
reason = mother_antnat_tfr$tfr_reason_text
tab = tabyl(reason) %>%
  arrange(-n) %>%
  mutate(percent = round(percent*100))
ftab = flextable(tab) %>%
  theme_box() %>%
  autofit()
ftab
```

# Mother A1C (AUSLAB data)

```{r}
for_table = select(mother_a1c, -ends_with('_id'), -source)
sumtable(for_table,
         title  = '',
         digits = 0)
```

### Mother A1C - histograms of continuous variables 

```{r}
for_plot = select_if(for_table, is.numeric) %>%
  pivot_longer(cols=everything())
gplot = ggplot(data=for_plot, aes(x=value))+
  geom_histogram()+
  facet_wrap(~name, scales='free')+
  theme_bw()
gplot
```


### Dates collected for A1C

```{r date_plot_a1c}
breaks = seq(min(mother_a1c$collected)-5, max(mother_a1c$collected)+5, 30)
dplot =  ggplot(mother_a1c, aes(x=collected)) + 
  geom_histogram(binwidth=30, colour="white", fill='skyblue') +
       scale_x_date(labels = date_format("%Y-%b"),
                    breaks = breaks) +
  ylab("Frequency") + 
  xlab("Year and Month") +
  theme_bw() + 
  theme(axis.text.x = element_text(angle=90), panel.grid.minor = element_blank())
dplot
```


# Mother glucose

```{r}
for_table = select(mother_glu, -ends_with('_id'), -source)
sumtable(for_table,
         title  = '',
         digits = 0)
```

### Mother glucose - histograms of continuous variables 

```{r}
for_plot = select_if(for_table, is.numeric) %>%
  pivot_longer(cols=everything())
gplot = ggplot(data=for_plot, aes(x=value))+
  geom_histogram()+
  facet_wrap(~name, scales='free')+
  theme_bw()
gplot
```

### Dates collected for glucose

```{r}
breaks = seq(min(mother_glu$collected)-5, max(mother_glu$collected)+5, 30)
dplot =  ggplot(mother_glu, aes(x=collected)) + 
  geom_histogram(binwidth=30, colour="white", fill='skyblue') +
       scale_x_date(labels = date_format("%Y-%b"),
                    breaks = breaks) +
  ylab("Frequency") + 
  xlab("Year and Month") +
  theme_bw() + 
  theme(axis.text.x = element_text(angle=90), panel.grid.minor = element_blank())
dplot
```