---
title: "Compare 2019 and 2020 gestional diabetes data"
output: html_document
author: "Adrian Barnett"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, comment='', dpi=400)
options(width=1000) # Wide pages
options(scipen=999) # avoid scientific presentation
library(ggplot2)
g.theme = theme_bw() + theme(panel.grid.minor = element_blank())
library(gridExtra)
library(dplyr)
library(lme4) # for model with random intercept
library(stargazer) # for nice regression tables in html
library(stringr)
library(flextable)
library(nimble) # for Bayesian models
source('99_functions.R')

# number of bootstraps
n_boot = 1000

## create outcomes in baby data
# SGA and LGA cut offs
load('data/ga_cut_offs.RData')
## full data
load('data/raw_data.RData') # from 0_read_data.R
baby_data = mutate(baby_data, gestation_weeks = floor(gestation)) %>%
  left_join(cut_offs, by=c('gestation_weeks','sex')) %>%
  mutate(
    twins_triplets = as.numeric(baby_data$plurality != 'Singleton'), # too few triplets to be their own category
    preterm = gestation_weeks < 37, 
         caesar = as.logical(labour_onset == 'No Labour (Caesarean Section)'), 
         sga = birth_weight < small_cut, # below 10th percentile
         lga = birth_weight > large_cut) # above 90th percentile
# remove data not needed to make things clearer
remove(baby_neonatal_treat, baby_resuscitation)

## get the mother data with new diagnosis
# select women based on their GDM diagnosis
# 2019 group
load('data/1_diagnosis_2019.RData')
g2019 = filter(diagnosis_2019, overall == 'No') %>%
  select(-overall)
# 2020 group
load('data/1_diagnosis_2020.RData')
g2020 = filter(diagnosis_2020, gdm == 'No diagnosis based on fasting blood glucose only') %>%
  select(-gdm)
# combine and create 2020 cohort; also add mother-level variables
mother = bind_rows(g2019, g2020, .id = 'group') %>%
  mutate(group_2020 = case_when(
    group == 1 ~ 0, # reference group of 2019
    group == 2 ~ 1
  ),
  nr_prev_caesar = ifelse(prev_pregnancies_flag == 'No', 0, nr_prev_caesar), # first pregnancy has no previous caesars
  age = baby_birth_year - mother_birth_year, # mother's age
  age10 = (age - 30)/10, # scaling
  body_mass_index5 = (body_mass_index - 25)/5,
  smoked_before_20wks = as.numeric(smoked_before_20wks == 'Yes'), # smoking has small categories like "not stated"'
  smoked_after_20wks = as.numeric(smoked_after_20wks == 'Yes')) %>%
  select(-group)

#### baby morbidity ##
baby_small = select(baby_data, 'mother_id', 'preg_seq_id','birth_id', 'preterm', 'sga','lga')
## distress
# assume if not in morbidity data that distress is FALSE
pattern = paste('Transient tachypnea of newborn','respiratory distress', collapse='|')
baby_distress = filter(baby_neonatal_morb, # has multiple rows per baby
 str_detect(neonatal_morbidity_code_text, pattern=pattern)) %>% 
  mutate(distress = TRUE)  %>%
  full_join(baby_small, by=c('mother_id', 'preg_seq_id','birth_id')) %>% # add preterm
  mutate(distress = ifelse(is.na(distress), FALSE, distress)) 

### hypoglycemia
pattern = 'Other neonatal hypoglycemia'  # check on "Other hypoglycemia"
baby_hypoglycemia = filter(baby_neonatal_morb, # has multiple rows per baby
 str_detect(neonatal_morbidity_code_text, pattern=pattern)) %>% 
  mutate(hypoglycemia = TRUE)  %>%
  full_join(baby_small, by=c('mother_id', 'preg_seq_id','birth_id')) %>% # add sga/lga
  mutate(hypoglycemia = ifelse(is.na(hypoglycemia), FALSE, hypoglycemia)) 


# blind results for cohort?
blind = TRUE

# finding variables
#dictionary[str_detect(tolower(dictionary$description), 'intrauterine'),]
```

This analysis compares perinatal complications between the 2020 group with "No GDM based on a FBGL < 4.7 mmol/l" with the 2019 group with "No GDM with an OGTT". The aim is to assess whether there was a difference in mother and baby outcomes for these two groups. We control for confounding using the variables identified in Nina's causal models. 

The key statistic is the difference in outcome for the 2020 group compared with the 2019 group together with the 95% confidence interval. The confidence interval is key as it describes the likely range of effects and so can be used to rule out clinically meaningful changes in risk. 

This initial version presents blinded results as the data on the birth group (2019 or 2020) has been scrambled meaning the results do not show the true differences for this predictor. Once the statistical models have been finalised, then birth group will be unscrambled.

The models used a random intercept for each mother to control for the correlation in outcomes for mothers who gave birth in both years.

<!--- The variable labelled "age10" is a 10 year increase in mother's age. --->

The variable labelled "body_mass_index5" is a 5 kg/m2 increase in mother's BMI.

There were too few triplets to analyse in their own category, so they were combined with twins.

## Birth weight

#### Regression model

```{r, results='asis'}
# causal diagram on page 211 (appendix F of Nina's thesis)
bw = run_model(outcome = 'birth_weight',
      predictors = c('body_mass_index5'),
      bdata = baby_data,
      dp = 0, 
      blind_outcome = blind)
stargazer(bw$model, 
          type = 'html',
          title = '',
          ci = TRUE,
          ci.separator = ' to ',
          digits = 0,
          report = 'vcs',
          single.row = TRUE,
          notes.append = FALSE,
          star.cutoffs = NA,
          omit.table.layout = "n",
          omit.stat = c('ll','aic','bic','f'))
```

#### Summary statistics (birth weight)

```{r}
bw$summary
```

#### Missing data (birth weight)

```{r}
bw$missing
```


## Gestational age at delivery (weeks)

#### Regression model

```{r, results='asis'}
# causal diagram on page 212 (appendix F of Nina's thesis) 
# iugr = intrauterine growth retardation
g_age = run_model(outcome = 'gestation',
      predictors = c("smoked_before_20wks","smoked_after_20wks",'twins_triplets'),
      bdata = baby_data,
      blind_outcome = blind)
stargazer(g_age$model, 
          type = 'html',
          title = '',
          ci = TRUE,
          ci.separator = ' to ',
          digits = 1,
          report = 'vcs',
          single.row = TRUE,
          notes.append = FALSE,
          star.cutoffs = NA,
          omit.table.layout = "n",
          omit.stat = c('ll','aic','bic','f'))
```

#### Summary statistics (gestational age)

```{r}
g_age$summary
```

#### Missing data (gestational age)

```{r}
g_age$missing
```

## Small for gestational age (SGA)

#### Regression model

```{r, results='asis'}
# causal diagram on page 212 (appendix F of Nina's thesis) 
# iugr = intrauterine growth retardation
sga = run_model(outcome = 'sga',
      predictors = c("smoked_before_20wks","smoked_after_20wks",'twins_triplets'),
      bdata = baby_data,
      check_clt = FALSE,
      binomial_outcome = FALSE,
      n_boot = n_boot,
      blind_outcome = blind)
stargazer(sga$model, 
          type = 'html',
          title = '',
          ci = TRUE,
          ci.separator = ' to ',
          digits = 1,
          report = 'vcs',
          single.row = TRUE,
          notes.append = FALSE,
          star.cutoffs = NA,
          omit.table.layout = "n",
          #apply.coef = exp,
          #apply.se = exp,
      omit.stat = c('ll','aic','bic','f'))
```

#### Summary statistics (SGA)

```{r}
sga$summary
```

#### Missing data (SGA)

```{r}
sga$missing
```


## Large for gestational age (LGA)

#### Regression model

```{r, results='asis'}
# causal diagram on page 212 (appendix F of Nina's thesis) 
# iugr = intrauterine growth retardation
lga = run_model(outcome = 'lga',
      predictors = c("smoked_before_20wks","smoked_after_20wks",'twins_triplets'),
      bdata = baby_data,
      check_clt = FALSE,
      binomial_outcome = FALSE,
      n_boot = n_boot,
      blind_outcome = blind)
stargazer(lga$model, 
          type = 'html',
          title = '',
          ci = TRUE,
          ci.separator = ' to ',
          digits = 1,
          report = 'vcs',
          single.row = TRUE,
          notes.append = FALSE,
          star.cutoffs = NA,
          omit.table.layout = "n",
          #apply.coef = exp,
          #apply.se = exp,
          omit.stat = c('ll','aic','bic','f'))
```

Model did not converge with twins and triplets as a predictor as almost every twin/triplet was not LGA.

#### Summary statistics (LGA)

```{r}
lga$summary
```

#### Missing data (LGA)

```{r}
lga$missing
```


## Caesarean delivery

This outcome comes from the variable "Labour onset" being equal to "No Labour (Caesarean Section)".

#### Regression model

```{r, results='asis'}
# causal diagram on page 212 (appendix F of Nina's thesis) 
# need to add breech/transvers
caesar = run_model(outcome = 'caesar',
      predictors = c("lga","nr_prev_caesar"),
      bdata = baby_data,
      check_clt = FALSE,
      binomial_outcome = FALSE,
      n_boot = n_boot,
      blind_outcome = blind)
stargazer(caesar$model, 
          type = 'html',
          title = '',
          ci = TRUE,
          ci.separator = ' to ',
          digits = 2,
          report = 'vcs',
          single.row = TRUE,
          notes.append = FALSE,
          star.cutoffs = NA,
          omit.table.layout = "n",
          omit.stat = c('ll','aic','bic','f'))
```

#### Summary statistics (caesar)

```{r}
caesar$summary
```

#### Missing data (caesar)

```{r}
caesar$missing
```


## Neonatal hypoglycaemia

```{r, results='asis'}
hypoglycemia = run_model(outcome = 'hypoglycemia',
      predictors = c("lga","sga","preterm"),
      bdata = baby_hypoglycemia,
      check_clt = FALSE,
      binomial_outcome = FALSE,
      n_boot = n_boot,
      blind_outcome = blind)
stargazer(hypoglycemia$model, 
          type = 'html',
          title = '',
          ci = TRUE,
          ci.separator = ' to ',
          digits = 2,
          report = 'vcs',
          single.row = TRUE,
          notes.append = FALSE,
          star.cutoffs = NA,
          omit.table.layout = "n",
          omit.stat = c('ll','aic','bic','f'))
```

#### Summary statistics (hypoglycemia)

```{r}
hypoglycemia$summary
```

#### Missing data (hypoglycemia)

```{r}
hypoglycemia$missing
```



## Gestational hypertension

_To come._

## Neonatal intensive or special care admission 

_To come._


# Summary plot

The plot shows the means and 95% confidence intervals for the estimated differences between the 2019 and 2020 groups. 

```{r}
# probabilities
to_plot = bind_rows(sga$g2020, lga$g2020, caesar$g2020, hypoglycemia$g2020)
pr_plot = ggplot(data=to_plot, aes(x=outcome, y=estimate, ymin=conf.low, ymax=conf.high))+
  geom_hline(lty=2, col='dark red', yintercept=0)+
  geom_point(col='darkseagreen', size=4)+
  geom_errorbar(col='darkseagreen', size=1.05, width=0)+
  coord_flip()+
  ylab('Probability difference')+
  xlab('')+
  ggtitle('Probabilities for binomial variables')+
  g.theme
# percent changes
to_plot = bind_rows(bw$g2020, g_age$g2020)
pc_plot = ggplot(data=to_plot, aes(x=outcome, y=estimate, ymin=conf.low, ymax=conf.high))+
  geom_hline(lty=2, col='dark red', yintercept=0)+
  geom_point(col='dodgerblue', size=4)+
  geom_errorbar(col='dodgerblue', size=1.05, width=0)+
  coord_flip()+
  ylab('Percent change')+
  xlab('')+
  ggtitle('Percent change for continuous variables')+
  g.theme
grid.arrange(pc_plot, pr_plot, ncol=1, heights=c(1,1.5))
```
