---
title: "Compare 2019 and 2020 gestional diabetes data"
output:
  word_document:
    reference_docx: "bmj-open-style.docx"
author: "Adrian Barnett"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, comment='', dpi=400)
options(width=1000) # Wide pages
options(scipen=999) # avoid scientific presentation
library(ggplot2)
g.theme = theme_bw() + theme(panel.grid.minor = element_blank())
library(gridExtra)
library(dplyr)
library(lme4) # for model with random intercept
library(stringr)
library(flextable)
library(nimble) # for Bayesian models
library(coda)
source('99_functions.R')
source("99_Bayes_models.R")

# number of bootstraps
n_boot = 1000

# causal diagrams from U:\Research\Projects\ihbi\aushsi\aushsi_barnetta\People\NinaM\thesis

## create outcomes in baby data
# SGA and LGA cut offs
load('data/ga_cut_offs.RData')
## full data
load('data/raw_data.RData') # from 0_read_data.R
baby_data = mutate(baby_data, gestation_weeks = floor(gestation)) %>%
  left_join(cut_offs, by=c('gestation_weeks','sex')) %>%
  mutate(
    twins_triplets = as.numeric(baby_data$plurality != 'Singleton'), # too few triplets to be their own category
    # outcomes:
    icn_scn_admission_flag = icn_scn_admission_flag == 'Yes', # special care nursery
    preterm = gestation_weeks < 37, 
    caesar = as.logical(labour_onset == 'No Labour (Caesarean Section)'), 
    sga = birth_weight < small_cut, # below 10th percentile
    lga = birth_weight > large_cut) # above 90th percentile
# remove data not needed to make things clearer
remove(baby_neonatal_treat, baby_resuscitation)

# add IUGR
iugr = filter(baby_neonatal_morb, neonatal_morbidity_code=='P059') %>%
  select(ends_with('_id')) %>%
  mutate(iugr = TRUE)
baby_data = left_join(baby_data, iugr, by=c('mother_id', 'preg_seq_id', 'birth_id')) %>%
  mutate(iugr = ifelse(is.na(iugr), FALSE, iugr))
  

## get the mother data with new diagnosis
# select women based on their GDM diagnosis
# 2019 group
load('data/1_diagnosis_2019.RData')
g2019 = filter(diagnosis_2019, overall == 'No') %>%
  select(-overall)
# 2020 group
load('data/1_diagnosis_2020.RData')
g2020 = filter(diagnosis_2020, gdm == 'No diagnosis based on fasting blood glucose only') %>%
  select(-gdm)
# combine and create 2020 cohort; also add mother-level variables
mother = bind_rows(g2019, g2020, .id = 'group') %>%
  mutate(group_2020 = case_when(
    group == 1 ~ 0, # reference group of 2019
    group == 2 ~ 1
  ),
  nr_prev_caesar = ifelse(prev_pregnancies_flag == 'No', 0, nr_prev_caesar), # first pregnancy has no previous caesars
  age = baby_birth_year - mother_birth_year, # mother's age
  age10 = (age - 30)/10, # scaling
  body_mass_index5 = (body_mass_index - 25)/5,
  smoked_before_20wks = as.numeric(smoked_before_20wks == 'Yes'), # smoking has small categories like "not stated"'
  smoked_after_20wks = as.numeric(smoked_after_20wks == 'Yes')) %>%
  select(-group)

## add outcome of gestational hypertension to mother data
gtn = filter(mother_preg_complicatn, str_detect(pregnancy_complication, '^O11|^O13|^O14|^O16')) %>%
  select(ends_with('_id')) %>%
  unique() %>% # because there can be multiple outcomes per mother
  mutate(gtn = TRUE)
mother = left_join(mother, gtn, by=c('mother_id','preg_seq_id')) %>%
    mutate(gtn = ifelse(is.na(gtn), FALSE, gtn)) 

#### baby morbidity ##
baby_small = select(baby_data, 'mother_id', 'preg_seq_id','birth_id', 'preterm', 'sga','lga')
## distress
# assume if not in morbidity data that distress is FALSE
pattern = paste(c('transient tachypnea of newborn','respiratory distress'), collapse='|')
baby_distress = filter(baby_neonatal_morb, # has multiple rows per baby
 str_detect(tolower(neonatal_morbidity_code_text), pattern=pattern)) %>% 
  select('mother_id', 'preg_seq_id','birth_id') %>%
  unique() %>% # because same baby can have multiple respiratory outcomes
  mutate(distress = TRUE) %>%
  full_join(baby_small, by=c('mother_id', 'preg_seq_id','birth_id')) %>% # add preterm
  mutate(distress = ifelse(is.na(distress), FALSE, distress)) 

### hypoglycemia
pattern = 'Other neonatal hypoglycemia'  # check on "Other hypoglycemia"
baby_hypoglycemia = filter(baby_neonatal_morb, # has multiple rows per baby
 str_detect(neonatal_morbidity_code_text, pattern=pattern)) %>% 
  mutate(hypoglycemia = TRUE)  %>%
  full_join(baby_small, by=c('mother_id', 'preg_seq_id','birth_id')) %>% # add sga/lga
  mutate(hypoglycemia = ifelse(is.na(hypoglycemia), FALSE, hypoglycemia)) 

# blind results for cohort?
blind = TRUE

# finding variables
#dictionary[str_detect(tolower(dictionary$description), 'intrauterine'),]
```

This analysis compares perinatal complications between the 2020 group with "No GDM based on a FBGL < 4.7 mmol/l" with the 2019 group with "No GDM with an OGTT". The aim is to assess whether there was a difference in mother and baby outcomes for these two groups. We attempt to control for confounding using the variables identified in Nina's causal models.

The models used a random intercept for each mother to control for the correlation in outcomes for mothers who gave birth in both years. We fitted models with and without an intercept and chose the most appropriate model for each outcome based on the Widely Applicable Information Criterion (WAIC) which balances model fit and complexity.

The models were fitted in a Bayesian paradigm so the key statistic is the 95% credible interval for the difference between the 2019 and 2020 groups. This interval has a 95% probability of containing the true difference, which is a much simpler interpretation that standard 95% confidence intervals. The key question is whether this interval includes or excludes clinically meaningful differences.

This initial version presents blinded results as the data on the birth group (2019 or 2020) has been scrambled meaning the results do not show the true differences for this predictor. Once the statistical models have been finalised, then birth group will be unscrambled.

<!--- The variable labelled "age10" is a 10 year increase in mother's age. --->

The variable labelled "body_mass_index5" is a 5 kg/m2 increase in mother's BMI.

There were too few triplets to analyse in their own category, so they were combined with twins.

##### page break

## Birth weight

```{r, include=FALSE}
file = c('results','birth_weight')
outfile = make_file(file)
if(outfile$exists == FALSE){
  # causal diagram on page 211 (appendix F of Nina's thesis)
  bw = run_model_bayes(outcome = 'birth_weight',
                 predictors = c('body_mass_index5'),
                 bdata = baby_data,
                 mdata = mother, 
                 dp = 0, 
                 blind_outcome = blind)
  save(bw, file = outfile$file)
}
if(outfile$exists == TRUE){
  load(outfile$file)
}
```

#### Model fit (birth weight)

```{r}
select(bw$model_fit, -outcome) %>%
  flextable() %>%
  theme_box() %>%
  colformat_double(j=2, digits = 1) %>%
  colformat_double(j=3, digits = 0) %>%
  autofit()
# for text
fit_with = filter(bw$model_fit, model=='With intercept') %>% pull(WAIC)
fit_without = filter(bw$model_fit, model=='Without intercept') %>% pull(WAIC)
diff = fit_with - fit_without
with_without = ifelse(diff < -2,'with','without')
# for best estimates
if(with_without == 'with'){
  bw$g2020 = filter(bw$g2020, with_intercept == TRUE)
  bw$table = filter(bw$table, with_intercept == TRUE)
}
if(with_without == 'without'){
  bw$g2020 = filter(bw$g2020, with_intercept == FALSE)
  bw$table = filter(bw$table, with_intercept == FALSE)
}
```

The smaller the WAIC the better the model. The column "pWAIC" is the estimated number of parameters.
The best model is the model `r with_without` the intercept for each mother.

#### Regression model (birth weight)

```{r}
ftab = bayes_table(bw$table) %>%
  flextable() %>%
  theme_box() %>%
  autofit()
ftab
```

"sd" is the standard deviation for the model error. 

#### Summary statistics (birth weight)

```{r}
bw$summary
```

#### Missing data (birth weight)

```{r}
bw$missing
```

##### page break

## Gestational age at delivery (weeks)


```{r, include=FALSE}
file = c('results','gestation')
outfile = make_file(file)
if(outfile$exists == FALSE){
# causal diagram on page 212 (appendix F of Nina's thesis) 
  g_age = run_model_bayes(outcome = 'gestation',
         predictors = c("smoked_before_20wks","smoked_after_20wks",'twins_triplets'),
         mdata = mother, 
         bdata = baby_data,
         dp = 1, 
         blind_outcome = blind)
  save(g_age, file = outfile$file)
}
if(outfile$exists == TRUE){
  load(outfile$file)
}
```

#### Model fit (birth weight)

```{r}
select(g_age$model_fit, -outcome) %>%
  flextable() %>%
  theme_box() %>%
  colformat_double(j=2, digits = 1) %>%
  colformat_double(j=3, digits = 0) %>%
  autofit()
# for text
fit_with = filter(g_age$model_fit, model=='With intercept') %>% pull(WAIC)
fit_without = filter(g_age$model_fit, model=='Without intercept') %>% pull(WAIC)
diff = fit_with - fit_without
with_without = ifelse(diff < -2,'with','without')
# for best estimates
if(with_without == 'with'){
  g_age$g2020 = filter(g_age$g2020, with_intercept == TRUE)
  g_age$table = filter(g_age$table, with_intercept == TRUE)
}
if(with_without == 'without'){
  g_age$g2020 = filter(g_age$g2020, with_intercept == FALSE)
  g_age$table = filter(g_age$table, with_intercept == FALSE)
}
```

The smaller the WAIC the better the model. The column "pWAIC" is the estimated number of parameters.
The best model is the model `r with_without` the intercept for each mother.

#### Regression model (gestational age)

```{r}
ftab = bayes_table(g_age$table, dp=2) %>%
  flextable() %>%
  theme_box() %>%
  autofit()
ftab
```

"sd.mother" is the standard deviation for random intercept for mothers. The larger this value, the more difference between mothers. 

#### Summary statistics (gestational age)

```{r}
g_age$summary
```

#### Missing data (gestational age)

```{r}
g_age$missing
```

##### page break

## Small for gestational age (SGA)

```{r, include=FALSE}
file = c('results','sga')
outfile = make_file(file)
if(outfile$exists == FALSE){
  # causal diagram on page 212 (appendix F of Nina's thesis) 
  sga = run_model_bayes(outcome = 'sga',
        predictors = c("iugr","smoked_before_20wks","smoked_after_20wks",'twins_triplets'),
        mdata = mother,
        bdata = baby_data,
        dp = 2,
        blind_outcome = blind)
  save(sga, file = outfile$file)
}
if(outfile$exists == TRUE){
  load(outfile$file)
}
```

#### Model fit (SGA)

```{r}
select(sga$model_fit, -outcome) %>%
  flextable() %>%
  theme_box() %>%
  colformat_double(j=2, digits = 1) %>%
  colformat_double(j=3, digits = 0) %>%
  autofit()
# for text
fit_with = filter(sga$model_fit, model=='With intercept') %>% pull(WAIC)
fit_without = filter(sga$model_fit, model=='Without intercept') %>% pull(WAIC)
diff = fit_with - fit_without
with_without = ifelse(diff < -2,'with','without')
# for best estimates
if(with_without == 'with'){
  sga$g2020 = filter(sga$g2020, with_intercept == TRUE)
  sga$table = filter(sga$table, with_intercept == TRUE)
}
if(with_without == 'without'){
  sga$g2020 = filter(sga$g2020, with_intercept == FALSE)
  sga$table = filter(sga$table, with_intercept == FALSE)
}
```

The smaller the WAIC the better the model. The column "pWAIC" is the estimated number of parameters.
The best model is the model `r with_without` the intercept for each mother.

#### Regression model (SGA)

```{r}
ftab = bayes_table(sga$table, dp=2) %>%
  flextable() %>%
  theme_box() %>%
  autofit()
ftab
# for text
text_mean = filter(sga$table, var=='twins_triplets') %>% pull(mean) %>% roundz(2)
```

The results are on the scale of probability. For example, the estimate for twins and triplets shows an increased probability of being small for gestational age of `r text_mean` compared with singletons. 

#### Summary statistics (SGA)

```{r}
sga$summary
```

#### Missing data (SGA)

```{r}
sga$missing
```

##### page break

## Large for gestational age (LGA)

```{r, include=FALSE}
# causal diagram on page 212 (appendix F of Nina's thesis) 
file = c('results','lga')
outfile = make_file(file)
if(outfile$exists == FALSE){
  # causal diagram on page 212 (appendix F of Nina's thesis) 
  # iugr = intrauterine growth retardation
  lga = run_model_bayes(outcome = 'lga',
      predictors = c("smoked_before_20wks","smoked_after_20wks",'twins_triplets'),
      mdata = mother,
      bdata = baby_data,
      dp = 2, 
      blind_outcome = blind)
  save(lga, file = outfile$file)
}
if(outfile$exists == TRUE){
  load(outfile$file)
}
```

#### Model fit (LGA)

```{r}
select(lga$model_fit, -outcome) %>%
  flextable() %>%
  theme_box() %>%
  colformat_double(j=2, digits = 1) %>%
  colformat_double(j=3, digits = 0) %>%
  autofit()
# for text
fit_with = filter(lga$model_fit, model=='With intercept') %>% pull(WAIC)
fit_without = filter(lga$model_fit, model=='Without intercept') %>% pull(WAIC)
diff = fit_with - fit_without
with_without = ifelse(diff < -2,'with','without')
# for best estimates
if(with_without == 'with'){
  lga$g2020 = filter(lga$g2020, with_intercept == TRUE)
  lga$table = filter(lga$table, with_intercept == TRUE)
}
if(with_without == 'without'){
  lga$g2020 = filter(lga$g2020, with_intercept == FALSE)
  lga$table = filter(lga$table, with_intercept == FALSE)
}
```

The smaller the WAIC the better the model. The column "pWAIC" is the estimated number of parameters.
The best model is the model `r with_without` the intercept for each mother.

#### Regression model (LGA)

```{r}
ftab = bayes_table(lga$table, dp=2) %>%
  flextable() %>%
  theme_box() %>%
  autofit()
ftab
```

#### Summary statistics (LGA)

```{r}
lga$summary
```

#### Missing data (LGA)

```{r}
lga$missing
```

##### page break

## Caesarean delivery

This outcome comes from the variable "Labour onset" being equal to "No Labour (Caesarean Section)".

```{r, include=FALSE}
# causal diagram on page 212 (appendix F of Nina's thesis) 
# need to add breech/transverse
file = c('results','caesar')
outfile = make_file(file)
if(outfile$exists == FALSE){
  # causal diagram on page 212 (appendix F of Nina's thesis) 
  # missing breech
  caesar = run_model_bayes(outcome = 'caesar',
                   predictors = c("body_mass_index5","lga","nr_prev_caesar"),
                   mdata = mother,
                   bdata = baby_data,
                   blind_outcome = blind)
  save(caesar, file = outfile$file)
}
if(outfile$exists == TRUE){
  load(outfile$file)
}
```

#### Model fit (caesar)

```{r}
select(caesar$model_fit, -outcome) %>%
  flextable() %>%
  theme_box() %>%
  colformat_double(j=2, digits = 1) %>%
  colformat_double(j=3, digits = 0) %>%
  autofit()
# for text
fit_with = filter(caesar$model_fit, model=='With intercept') %>% pull(WAIC)
fit_without = filter(caesar$model_fit, model=='Without intercept') %>% pull(WAIC)
diff = fit_with - fit_without
with_without = ifelse(diff < -2,'with','without')
# for best estimates
if(with_without == 'with'){
  caesar$g2020 = filter(caesar$g2020, with_intercept == TRUE)
  caesar$table = filter(caesar$table, with_intercept == TRUE)
}
if(with_without == 'without'){
  caesar$g2020 = filter(caesar$g2020, with_intercept == FALSE)
  caesar$table = filter(caesar$table, with_intercept == FALSE)
}
```

The smaller the WAIC the better the model. The column "pWAIC" is the estimated number of parameters.
The best model is the model `r with_without` the intercept for each mother.

#### Regression model (caesar)

```{r}
ftab = bayes_table(caesar$table, dp=2) %>%
  flextable() %>%
  theme_box() %>%
  autofit()
ftab
```

#### Summary statistics (caesar)

```{r}
caesar$summary
```

#### Missing data (caesar)

```{r}
caesar$missing
```

##### page break

## Neonatal hypoglycaemia

```{r, include=FALSE}
file = c('results','hypoglycemia')
outfile = make_file(file)
if(outfile$exists == FALSE){
  # causal diagram on page 212 (appendix F of Nina's thesis) 
  # iugr = intrauterine growth retardation
  hypoglycemia = run_model_bayes(outcome = 'hypoglycemia',
                   predictors = c("lga","sga","preterm"),
                   mdata = mother,
                   bdata = baby_hypoglycemia,
                   blind_outcome = blind)
  save(hypoglycemia, file = outfile$file)
}
if(outfile$exists == TRUE){
  load(outfile$file)
}
```

#### Model fit (hypoglycemia)

```{r}
select(hypoglycemia$model_fit, -outcome) %>%
  flextable() %>%
  theme_box() %>%
  colformat_double(j=2, digits = 1) %>%
  colformat_double(j=3, digits = 0) %>%
  autofit()
# for text
fit_with = filter(hypoglycemia$model_fit, model=='With intercept') %>% pull(WAIC)
fit_without = filter(hypoglycemia$model_fit, model=='Without intercept') %>% pull(WAIC)
diff = fit_with - fit_without
with_without = ifelse(diff < -2,'with','without')
# for best estimates
if(with_without == 'with'){
  hypoglycemia$g2020 = filter(hypoglycemia$g2020, with_intercept == TRUE)
  hypoglycemia$table = filter(hypoglycemia$table, with_intercept == TRUE)
}
if(with_without == 'without'){
  hypoglycemia$g2020 = filter(hypoglycemia$g2020, with_intercept == FALSE)
  hypoglycemia$table = filter(hypoglycemia$table, with_intercept == FALSE)
}
```

The smaller the WAIC the better the model. The column "pWAIC" is the estimated number of parameters.
The best model is the model `r with_without` the intercept for each mother.

#### Regression model (hypoglycemia)

```{r}
ftab = bayes_table(hypoglycemia$table, dp=2) %>%
  flextable() %>%
  theme_box() %>%
  autofit()
ftab
```

#### Summary statistics (hypoglycemia)

```{r}
hypoglycemia$summary
```

#### Missing data (hypoglycemia)

```{r}
hypoglycemia$missing
```


## Gestational hypertension

Maternal hypertension.

```{r, include=FALSE}
file = c('results','gtn')
outfile = make_file(file)
if(outfile$exists == FALSE){
  # causal diagram on page 214
  gtn = run_model_bayes(outcome = 'gtn',
                 predictors = c('body_mass_index5',"smoked_before_20wks","smoked_after_20wks",'twins_triplets'),
                 bdata = baby_data,
                 mdata = mother, 
                 blind_outcome = blind)
  save(gtn, file = outfile$file)
}
if(outfile$exists == TRUE){
  load(outfile$file)
}
```

#### Model fit (gestational hypertension)

```{r}
select(gtn$model_fit, -outcome) %>%
  flextable() %>%
  theme_box() %>%
  colformat_double(j=2, digits = 1) %>%
  colformat_double(j=3, digits = 0) %>%
  autofit()
# for text
fit_with = filter(gtn$model_fit, model=='With intercept') %>% pull(WAIC)
fit_without = filter(gtn$model_fit, model=='Without intercept') %>% pull(WAIC)
diff = fit_with - fit_without
with_without = ifelse(diff < -2,'with','without')
# for best estimates
if(with_without == 'with'){
  gtn$g2020 = filter(gtn$g2020, with_intercept == TRUE)
  gtn$table = filter(gtn$table, with_intercept == TRUE)
}
if(with_without == 'without'){
  gtn$g2020 = filter(gtn$g2020, with_intercept == FALSE)
  gtn$table = filter(gtn$table, with_intercept == FALSE)
}
```

The smaller the WAIC the better the model. The column "pWAIC" is the estimated number of parameters.
The best model is the model `r with_without` the intercept for each mother.

#### Regression model (gestational hypertension)

```{r}
ftab = bayes_table(gtn$table, dp=2) %>%
  flextable() %>%
  theme_box() %>%
  autofit()
ftab
```

"sd" is the standard deviation for the model error. 

#### Summary statistics (gestational hypertension)

```{r}
gtn$summary
```

#### Missing data (gestational hypertension)

```{r}
gtn$missing
```

##### page break

## Neonatal intensive or special care admission 

```{r, include=FALSE}
file = c('results','nicu')
outfile = make_file(file)
if(outfile$exists == FALSE){
  # causal diagram on page 211 (appendix F of Nina's thesis)
  nicu = run_model_bayes(outcome = 'icn_scn_admission_flag',
                 predictors = c('body_mass_index5'),
                 bdata = baby_data,
                 mdata = mother, 
                 blind_outcome = blind)
  save(nicu, file = outfile$file)
}
if(outfile$exists == TRUE){
  load(outfile$file)
}
```

#### Model fit (neonatal intensive or special care admission)

```{r}
select(nicu$model_fit, -outcome) %>%
  flextable() %>%
  theme_box() %>%
  colformat_double(j=2, digits = 1) %>%
  colformat_double(j=3, digits = 0) %>%
  autofit()
# for text
fit_with = filter(nicu$model_fit, model=='With intercept') %>% pull(WAIC)
fit_without = filter(nicu$model_fit, model=='Without intercept') %>% pull(WAIC)
diff = fit_with - fit_without
with_without = ifelse(diff < -2,'with','without')
# for best estimates
if(with_without == 'with'){
  nicu$g2020 = filter(nicu$g2020, with_intercept == TRUE)
  nicu$table = filter(nicu$table, with_intercept == TRUE)
}
if(with_without == 'without'){
  nicu$g2020 = filter(nicu$g2020, with_intercept == FALSE)
  nicu$table = filter(nicu$table, with_intercept == FALSE)
}
```

The smaller the WAIC the better the model. The column "pWAIC" is the estimated number of parameters.
The best model is the model `r with_without` the intercept for each mother.

#### Regression model (neonatal intensive or special care admission)

```{r}
ftab = bayes_table(nicu$table, dp=2) %>%
  flextable() %>%
  theme_box() %>%
  autofit()
ftab
```

"sd" is the standard deviation for the model error. 

#### Summary statistics (neonatal intensive or special care admission)

```{r}
nicu$summary
```

#### Missing data (neonatal intensive or special care admission)

```{r}
nicu$missing
```

##### page break

## Respiratory distress 

```{r, include=FALSE}
file = c('results','distress')
outfile = make_file(file)
if(outfile$exists == FALSE){
  # causal diagram on page 211 (appendix F of Nina's thesis)
  distress = run_model_bayes(outcome = 'distress',
                         predictors = c('body_mass_index5'),
                         bdata = baby_distress,
                         mdata = mother, 
                         blind_outcome = blind)
  save(distress, file = outfile$file)
}
if(outfile$exists == TRUE){
  load(outfile$file)
}
```

#### Model fit (respiratory distress)

```{r}
select(distress$model_fit, -outcome) %>%
  flextable() %>%
  theme_box() %>%
  colformat_double(j=2, digits = 1) %>%
  colformat_double(j=3, digits = 0) %>%
  autofit()
# for text
fit_with = filter(distress$model_fit, model=='With intercept') %>% pull(WAIC)
fit_without = filter(distress$model_fit, model=='Without intercept') %>% pull(WAIC)
diff = fit_with - fit_without
with_without = ifelse(diff < -2,'with','without')
# for best estimates
if(with_without == 'with'){
  distress$g2020 = filter(distress$g2020, with_intercept == TRUE)
  distress$table = filter(distress$table, with_intercept == TRUE)
}
if(with_without == 'without'){
  distress$g2020 = filter(distress$g2020, with_intercept == FALSE)
  distress$table = filter(distress$table, with_intercept == FALSE)
}
```

The smaller the WAIC the better the model. The column "pWAIC" is the estimated number of parameters.
The best model is the model `r with_without` the intercept for each mother.

#### Regression model (respiratory distress)

```{r}
ftab = bayes_table(distress$table, dp=2) %>%
  flextable() %>%
  theme_box() %>%
  autofit()
ftab
```

"sd" is the standard deviation for the model error. 

#### Summary statistics (respiratory distress)

```{r}
distress$summary
```

#### Missing data (respiratory distress)

```{r}
distress$missing
```

##### page break

# Summary plot

The plot shows the means and 95% confidence intervals for the estimated differences between the 2019 and 2020 groups. 

```{r, fig.height=7}
# probabilities
labels1 = c('SGA','LGA','Caesarean','Hypoglycemia','Gestational\nhypertension','NICU/SCN','Respiratory\ndistress')
labels2 = c('Birthweight','Gestational age')
to_plot = bind_rows(sga$g2020, lga$g2020, caesar$g2020, hypoglycemia$g2020, gtn$g2020, nicu$g2020, distress$g2020, .id = 'outcome') %>%
  mutate(outcome = factor(outcome, levels=1:7, labels=labels1))
pr_plot = ggplot(data=to_plot, aes(x=outcome, y=mean, ymin=lower, ymax=upper))+
  geom_hline(lty=2, col='dark red', yintercept=0)+
  geom_point(col='darkseagreen', size=4)+
  geom_errorbar(col='darkseagreen', size=1.05, width=0)+
  coord_flip()+
  ylab('Probability difference')+
  xlab('')+
  ggtitle('Probabilities for binomial variables')+
  g.theme
## percent changes
bw_change = make_percent_change(bw$table)
g_age_change = make_percent_change(g_age$table)
to_plot = bind_rows(bw_change, g_age_change, .id = 'outcome') %>%
  mutate(outcome = factor(outcome, levels=1:2, labels=labels2))
pc_plot = ggplot(data=to_plot, aes(x=outcome, y=mean, ymin=lower, ymax=upper))+
  geom_hline(lty=2, col='dark red', yintercept=0)+
  geom_point(col='dodgerblue', size=4)+
  geom_errorbar(col='dodgerblue', size=1.05, width=0)+
  coord_flip()+
  ylab('Percent change')+
  xlab('')+
  ggtitle('Percent change for continuous variables')+
  g.theme
grid.arrange(pc_plot, pr_plot, ncol=1, heights=c(1,1.7))
```
